Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

Thus, for this combined subsetting and data access operation the on-disk backend
performed better than the in-memory `MSnExp`, while even requiring much less
memory.

>>>>

For this combined subsetting and data access operation the on-disk backend
performed better than the in-memory `MSnExp`, while even requiring much less
memory.
